{{< var titll >}}

### 2024-11-15 docs/analyzer.qmd
rec

```{webr-r}
#| echo: fenced
#| eval: true
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
library(ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
#ls(package:ManifoldDestinyWASMP)
#data(package='ManifoldDestinyWASMD')
apps <- appn0
```

```{webr-r}
adat <- apps[[1]]
amet <- apps[[2]]
cob <- Countinggraphs(adat)
cob$purging(z=0) 
def <- Estimation(cob$rdfce)
```

>>>>

```{webr-r}
#| echo: fenced
#| eval: true
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
library(ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
ls(package:ManifoldDestinyWASMP)
data(package='ManifoldDestinyWASMD')
```

```{webr-r}
#apps <- appn0
#adat <- apps[[1]]
#amet <- apps[[2]]
#cob <- Countinggraphs(adat)
#cob$purging(z=0) 
#def <- Estimation(cob$rdfce)
```
